Figure 3c

### 2017-12-06 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
added linear model for growth exp.

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

@@

#unreported p-values per time point
p <- data %>% 
  filter(Time != 0) %>% 
  unite(tmp, `Biological Replicate`, `Cell line`) %>% 
  spread(tmp, techMean) %>% 
  group_by(Treatment, Time) %>% 
  summarize(
	  p = t.test(
	    c(`1_PC3 miR34a asRNA`, `2_PC3 miR34a asRNA`, `3_PC3 miR34a asRNA`), 
	    c(`1_PC3 Mock`, `2_PC3 Mock`, `3_PC3 Mock`)
	  )$p.value,
	  meanAS = mean(c(`1_PC3 miR34a asRNA`, `2_PC3 miR34a asRNA`, `3_PC3 miR34a asRNA`)),
	  meanMock = mean(c(`1_PC3 Mock`, `2_PC3 Mock`, `3_PC3 Mock`))
  ) %>%
  mutate(fold = meanAS / meanMock)
```

>>>>

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable",
    "broom"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

@@

#linear model
model.data <-  data %>%
  mutate(Time = as.numeric(Time)) %>%
  group_by(Treatment) %>%
  mutate(rank = rank(techMean)) %>%
  do(glance(lm(rank ~ Time +`Cell line`, data = .))) %>%
  ungroup() %>%
  rename(pValue = p.value) %>%
  pFormat(.) %>%
  select(-pValue) %>%
  rename(p.value = pFormat)

as.data.frame(model.data)

growth.lm <- data %>%
  mutate(Time = as.numeric(Time)) %>%
  group_by(Treatment) %>%
  mutate(rank = rank(techMean)) %>%
  do(tidy(lm(rank ~ Time +`Cell line`, data = .))) %>%
  ungroup() %>%
  rename(pValue = p.value) %>%
  pFormat(.) %>%
  select(-pValue) %>%
  rename(p.value = pFormat)

as.data.frame(growth.lm)
